The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-16 dit-paper_ieee.tex
added reference
algo 1 review

		\begin{algorithm}
			\caption{Modified Gauss Algorithm}
			\label{alg:multiACRP}
			\begin{algorithmic}[1]
				\REQUIRE $\forall j: A_j$ is a list of the sets of possible $a_i$ values for
				task $\tau_j$ 
				\REQUIRE $H$ is the hyperperiod of the system

				\STATE $sumchunks \leftarrow \text{empty list}$
				\FORALL{$\tau_j \in \tau$}
					\STATE $taskTerms \leftarrow \text{empty list}$
					\STATE $Mj \leftarrow \frac{H}{T_j}$
					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_j)$
					\FORALL{$a_i \in A_j$}
						\STATE $taskTerms[i] \leftarrow (a_i \cdot Mj \cdot invMj)$
					\ENDFOR
					\STATE $sumchunks[j] \leftarrow taskTerms$
				\ENDFOR

				\STATE $results \leftarrow \text{empty list}$
				\STATE append $0$ to $results$
				\FORALL{$\tau_j \in \tau$}
					\STATE $newresults \leftarrow \text{empty list}$
					\FORALL{$a_i \in A_j$}
						\FORALL{$r \in results$}
							\STATE $\text{append} \; (r + sumchunks[j][i]) \; \text{to} \;
							newresults$
						\ENDFOR
					\ENDFOR
					\STATE $results \leftarrow newresults$
				\ENDFOR
				\RETURN $r \; (mod \; H)$ for all $r \in results$
			\end{algorithmic}
		\end{algorithm}

@@

		The description we presented in Section \ref{sct:cspaceDescr} was general, and
		is thus still relevant. Therefore the C-space is still accurately described by
		the following infinite number of constraints:

>>>>

		\begin{algorithm}
			\caption{Modified Gauss Algorithm}
			\label{alg:multiACRP}
			\begin{algorithmic}[1]
				\REQUIRE $\forall i: A_i$ is the set of possible $a_i$ values for
					task $\tau_i$
				\REQUIRE $H$ is the hyperperiod of the system

				\STATE $sumchunks \leftarrow \text{empty list}$
				\FORALL{$\tau_i \in \tau$}
					\STATE $taskTerms \leftarrow \text{empty list}$
					\STATE $Mj \leftarrow \frac{H}{T_i}$
					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_i)$
					\FORALL{$a_i \in A_i$}
						\STATE append $(a_i \cdot Mj \cdot invMj)$ to $taskTerms$
					\ENDFOR
					\STATE $sumchunks[i] \leftarrow taskTerms$
				\ENDFOR

				\STATE $results \leftarrow \text{empty list}$
				\STATE append $0$ to $results$
				\FORALL{$\tau_i \in \tau$}
					\STATE $newresults \leftarrow \text{empty list}$
					\FORALL{$chunk \in sumchunks[i]$}
						\FORALL{$r \in results$}
							\STATE $\text{append} \; (r + chunk) \; \text{to} \; newresults$
						\ENDFOR
					\ENDFOR
					\STATE $results \leftarrow newresults$
				\ENDFOR
				\RETURN $r \; (mod \; H)$ for all $r \in results$
			\end{algorithmic}
		\end{algorithm}

@@

		The description we presented in Section \ref{sct:cspaceDescr} based on \cite{baruah1999generalized} was general, and
		is thus still relevant. Therefore the C-space is still accurately described by
		the following infinite number of constraints:
